### 2020-06-01 writeup/proof_examples.tex
revisions

\subsection{Proofs for Section \ref{sec_similarity}}\label{app_proof_31}

For the ratio $w=w_1/w_2$, we define the function
\begin{align}
	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + (n_1 w^2 +n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{eq_val_mtl},
\be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
with high probability for any constant $\e>0$. Thus for the following discussions, it suffices focus on the behavior of $\val (w)$. Let $\hat w$ the minimizer of $\val(w)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} gives that $|\hat v - \hat w|=\OO(p^{-1/2+\e})$ whp.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result.
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
We have that the minimizer for $\val(w)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

Then we prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

@@

 Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.

@@

\subsection{Proofs for Section \ref{sec_benefit}}\label{app_proof_data}

 We first prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
\end{proposition}

>>>>

\subsection{Supplement to Section \ref{sec_similarity}}\label{app_proof_31}

For the ratio $w=w_1/w_2$, we define the function
\begin{align}
	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + (n_1 w^2 +n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
\cor Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{approxvalid},
\be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
with high probability for any constant $\e>0$. \nc Thus for the following discussions, it suffices focus on the behavior of $\val (w)$. Let $\hat w$ the minimizer of $\val(w)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} gives that $|\hat v - \hat w|=\OO(p^{-1/2+\e})$ whp.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result.
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
We have that the minimizer for $\val(w)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

\subsection{Supplement to Section \ref{sec_datasize}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

@@

Then we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio, denoted as $x^\star$.

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Then the data efficiency ratio $x^\star$ satifies 
	\[ \al_l - \oo(1) \le x^\star\le \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}}, \]
	where we denoted
	$$\al_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
\end{proposition}

\subsection{Supplement to Section \ref{sec_covshift}}\label{app_proof_33}

% Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.

@@

\subsection{Labeled data de-noising}\label{app_proof_data}
